Paradigms in Physics 2.0

### 2018-09-29 proposal.tex
Final changes, from Emily, etc.

\newcommand\evzsays[1]{\textcolor{red}{[\sc EvZ: {\em#1}]}}
\newcommand\davidsays[1]{\textcolor{blue}{[\sc DR: {\em#1}]}}

@@

In 2016, the Department of Physics at Oregon State University began a
process to revise our Paradigms in Physics curriculum for physics
majors. Paradigms~2.0 began in the Winter of 2016, after the faculty agreed to undertake this reform during the previous year. The process included frequent meetings by a small committee of faculty volunteers, a colloquium to communicate plans and to request assistance, an online survey of students and faculty to identify issues, individual interviews with the faculty teaching each course, and discussions with focus groups of students and instructional faculty.

As we developed ideas to address challenges in the curriculum, we met with each faculty member individually to explain and refine our proposal. Major changes included revising a series of courses, eliminating others, re-conceptualizing how to integrate just-in-time mathematics instruction, and introducing two sophomore-year courses designed specifically to help prepare students for their upper-division courses. The proposal was unanimously approved by the faculty and then implemented during 2016-2017.

This paper will describe both the process of the reform and its
outcome. It will provide a coarse-grained picture of how one department achieved a broad-scale reform of its upper-division curriculum, which can serve as a valuable balance to the more fine-grained view that is needed for refining classroom activities or revising a single course.  In addition to the Paradigms 2.0 reform, we will briefly introduce the original effort that began in 1996 \cite{manogue2001paradigms,manogue2003paradigms}, and summarize how that reform was maintained and refined during the intervening decades. Few departments embark on such a long-term endeavor and publishing a report on how we managed this may be helpful for others seeking to reform their curriculum.

@@

\paragraph*{Research questions}
\begin{itemize}
\item What was the culture of the department when the faculty initiated revising the upper-level physics curriculum? In
  particular, what were the participants' beliefs about teaching and
  learning?
\item What motivated making changes and how did the faculty form a
  coherent vision for the revised program?
\item How did the faculty develop and communicate plans for this revised
  curriculum?
\item How have they changed instruction based upon the proposals that
  the faculty approved with an unanimous vote?
\end{itemize}
\paragraph*{Research methods}
Data included audio recordings of interviews with faculty before, during and after the Paradigms 2.0 process; responses to an online survey of students and faculty; audio recordings, notes, and some photos during Paradigms 2.0 Committee meetings, Upper Division Curriculum Committee meetings, and some faculty meetings; and copies of relevant documents. Analysis included a quantitative summary of survey data and qualitative interpretations of what happened while initiating and sustaining the Paradigms in Physics program (1996-2015), re-envisioning the Paradigms Program during 2016, and implementing Paradigms 2.0 during 2016-2017 and beyond.

>>>>

\newcommand\camsays[1]{\textcolor{red}{[\sc CAM: {\em#1}]}}
\newcommand\evzsays[1]{\textcolor{red}{[\sc EvZ: {\em#1}]}}
\newcommand\davidsays[1]{\textcolor{blue}{[\sc DR: {\em#1}]}}

@@

In 2016, the Department of Physics at Oregon State University began a
process to revise our award-winning Paradigms in Physics curriculum for physics
majors. Paradigms~2.0 began in the Winter of 2016. The process included frequent meetings by a small committee of faculty volunteers, a colloquium to communicate plans and to request assistance, an online survey of students and faculty to identify issues, individual interviews with faculty teaching each course, and discussions with focus groups of students and faculty.

As we developed ideas to address identified challenges in the curriculum, we met with each faculty member individually to explain and refine our proposal. Major changes included revising a series of courses, eliminating others, re-conceptualizing how to integrate just-in-time mathematics instruction, and introducing two sophomore-year courses designed specifically to help prepare students for their upper-division courses. The proposal was unanimously approved by the faculty and implemented during 2016-2017.

This paper describes both our research about the process of the reform and its
outcome. It shows how one department achieved a broad-scale reform of its upper-division curriculum, which can serve as a valuable balance to the more fine-grained view that is needed for designing/refining classroom activities or revising a single course.  In addition, we briefly summarize how the original effort began\cite{manogue2001paradigms,manogue2003paradigms}, was initiated and sustained over  two decades\cite{vanzeeHistory}. Few departments embark on such a long-term endeavor and publishing a report on how we managed this may be helpful for others seeking to reform their curriculum and sustain their changes in a flexible, organic way.

@@

\paragraph*{Research questions}
\begin{itemize}
\item What was the culture of the department when the faculty initiated revising the upper-level physics curriculum? In particular, what were the participants' beliefs about teaching and learning?
\item What motivated making changes and how did the faculty form a
  coherent vision for the revised program?
\item How did the faculty develop and communicate plans for this revised
  curriculum?
\item How have they changed instruction based upon the proposals that
  the faculty approved with a unanimous vote?
\end{itemize}
\paragraph*{Research methods}
Data included audio recordings of interviews with faculty before, during and after the Paradigms 2.0 process; responses to an online survey of students and faculty; audio recordings, notes, and some photos during Paradigms 2.0 Committee meetings, Upper Division Curriculum Committee meetings, and some faculty meetings; and copies of relevant documents. Analysis included a quantitative summary of survey data and qualitative interpretations of what happened while initiating and sustaining the Paradigms in Physics program (1996-2015), re-envisioning the Paradigms Program during 2016, and implementing Paradigms 2.0 during 2016-2017 and beyond.
